Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-07-10 SUBMISSION/article/article.tex
Commit 2024-07-10 11:13

The distribution of the number of CE events as a function of OIR is
shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
there is an inverse relationship between the frequency of CE events and
OIR with an exponential-like decline. This is expected, as the stronger
the CE events are, the rarer the conditions favoring the occurrence of
CE events. For the majority (over \(62\,\%\)) of the CE events the OIR
is below the long-term average of \(39.9 \, \text{W} / \text{m}^2\),
while about \(8.1\,\%\) of the events correspond to OIR larger than
\(100\,\text{W}/\text{m}^2\) and up to the highest value of
\(412.4\,\text{W}/\text{m}^2\). This distribution is indicative of the
magnitude and the probability of the expected CE events over
Thessaloniki. Similar distribution of CE events, albeit with larger OIR
values, has been reported by \citet{Vamvakas2020}, for the city of
Patras. This site is located \(2.5^\circ\) south of Thessaloniki and is
exposed to air masses coming mainly from the eastern Mediterranean
resulting in different cloud patterns, that may affect the
characteristics and magnitude of the CE events.

@@

\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023. The histogram was splited in two plots with differnt y-axis limits for better readability.}\label{fig:ceg-duration-distribution}
\end{figure}

>>>>

The distribution of the number of CE events as a function of OIR is
shown in Figure\nobreakspace{}\ref{fig:ovir-distribution}. Apparently,
there is an inverse relationship between the frequency of CE events and
OIR with an exponential-like decline. This is expected, as the stronger
the CE events are, the rarer the conditions favoring the occurrence of
CE events. For the majority (over \(62\,\%\)) of the CE events the OIR
is below the long-term average of \(39.9\,\text{W}/\text{m}^2\), while
about \(8.1\,\%\) of the events correspond to OIR larger than
\(100\,\text{W}/\text{m}^2\) and up to the highest value of
\(412.4\,\text{W}/\text{m}^2\). This distribution is indicative of the
magnitude and the probability of the expected CE events over
Thessaloniki. Similar distribution of CE events, albeit with larger OIR
values, has been reported by \citet{Vamvakas2020}, for the city of
Patras. This site is located \(2.5^\circ\) south of Thessaloniki and is
exposed to air masses coming mainly from the eastern Mediterranean
resulting in different cloud patterns, that may affect the
characteristics and magnitude of the CE events.

@@

\caption{Relative frequency distribution of CE groups of consequent CE events according to their duration for Thessaloniki in the period 1993 -- 2023. The histogram was split in two plots with different y-axis scales for better readability.}\label{fig:ceg-duration-distribution}
\end{figure}
